# packgraph

<!-- badges: start -->
[![R build status](https://github.com/mpadge/packgraph/workflows/R-CMD-check/badge.svg)](https://github.com/mpadge/packgraph/actions)
[![Travis build status](https://travis-ci.org/mpadge/packgraph.svg?branch=master)](https://travis-ci.org/mpadge/packgraph)
[![Project Status: Concept](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

Examine and analyse static function call graphs of R packages. Mostly derived
from functionality provided by the [`r-lib/pkgapi`
package](https://github.com/r-lib/pkgapi), which is not on CRAN and must first
be installed with

```{r pkgapi, eval = FALSE}
remotes::install_github ("r-lib/pkgapi")
```

The main function, `pg_graph()`, returns all exported and non-exported
functions from a package (as `nodes`), and tallies of all functional
connections between these (as `edges`). The function also includes a `plot`
parameter which can be used to visualize the resultant network using the
[`visNetwork` package](https://github.com/datastorm-open/visNetwork).

```{r example, eval = TRUE}
library (packgraph)
if (!file.exists ("./git2r"))
    git2r::clone ("https://github.com/ropensci/git2r", local_path = "./git2r")
# Currently needs absolute file paths to work
pkg_dir <- tools::file_path_as_absolute ("./git2r")
g <- pg_graph (pkg_dir, plot = FALSE)
g
```

# prior art

- Much of the functionality is primarily built upon the [`pkgapi`
  package](https://github.com/r-lib/pkgapi).
- The [`flow` package](https://github.com/moodymudskipper/flow) produces flow diagrams of R functions.
- The [`collaboratoR` package](https://github.com/bupaverse/collaborateR) as
  presented at [eRum
  2020](https://milano-r.github.io/erum2020program/regular-talks.html#using-process-mining-principles-to-extract-a-collaboration-graph-from-a-version-control-system-log)
  extracts graphs of *collaborators* from a version control history rather than
  graphs of functions.
