# packgraph

<!-- badges: start -->
[![R build status](https://github.com/mpadge/packgraph/workflows/R-CMD-check/badge.svg)](https://github.com/mpadge/packgraph/actions)
[![Travis build status](https://travis-ci.org/mpadge/packgraph.svg?branch=master)](https://travis-ci.org/mpadge/packgraph)
[![Project Status: Concept](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

Examine and analyse static function call graphs of R packages. Mostly derived
from functionality provided by the [`r-lib/pkgapi`
package](https://github.com/r-lib/pkgapi), which is not on CRAN and must first
be installed with
```{r pkgapi, eval = FALSE}
source("https://install-github.me/r-lib/pkgapi")
```
(or `remotes::install_github()` will also work).

Currently contains a single function, `pg_graph()`, which returns all exported
and non-exported functions from a package (as `nodes`), and tallies of all
functional connections between these (as `edges`). The function also includes
a `plot` parameter which can be used to visualize the resultant network using
the [`visNetwork` package](https://github.com/datastorm-open/visNetwork).

```{r example, eval = FALSE}
git2r::clone ("https://github.com/ropensci/git2r", local_path = "./git2r")
# Currently needs absolute file paths to work
pkg_dir <- tools::file_path_as_absolute ("./git2r")
g <- pg_graph (pkg_dir, plot = FALSE)
g
```
```{r example-fakey, echo = FALSE}
id <- c (".onUnload", "[.git_tree", "add", "add_session_info", "ahead_behind",
         "as.character.git_time", "as.data.frame.git_commit",
         "as.data.frame.git_repository", "as.data.frame.git_tree",
         "as.list.git_tree", rep (NA, 158))
nodes <- tibble::tibble (id = id, label = id, export = FALSE, group = 1)
nodes$export [c (3, 5)] <- TRUE


from <- c ("[.git_tree", "add", "add", "ahead_behind",
           "as.data.frame.git_repository", "as.list.git_tree", "blame",
           "blob_create", "branches", "bundle_r_package", rep (NA, 192))
to <- c ("lookup", "lookup_repository", "workdir", "lookup_commit", "commits",
         "lookup", "lookup_repository", "lookup_repository",
         "lookup_repository", "clone", rep (NA, 192))
n <- rep (1, 202)
n [4] <- 2
edges <- tibble::tibble (from = from, to = to, n = n)

list (nodes = nodes, edges = edges)
```



